HEP Software Foundation Community White Paper Working Group -- Training, Staffing and Careers

### 2018-06-21 CWP/papers/HSF-CWP-2017-02_training/latex/cwp-wg-training-careers.tex
Improve English expression regarding challenegs

%____________________________________________________________________
%____________________________________________________________________
\section{Motivation for some HSF coordinated actions}

@@

Within a single experiment, different skill sets are needed. In addition to a
skill set that contains basic programming language knowledge, testing and code
management tools, and experiment-specific framework knowledge, there are more
specialized skills that only a subset of the community needs to know, such as
software optimization, or low-level hardware interfaces.
While there already are experiment-specific training efforts in place, there are
many needs that are in common between experiments. Therefore, we should probably
strive to extract the common knowledge and build a common training program. This
would reduce duplication of efforts and enable growth of a shared training
culture by accumulating and sharing expertise across different experiments.

To realise this goal, a possibility could be the institution of a {\em
federation} of existing training initiatives, a very lightwheight umbrella just
aimed at improving the efficiency and cost-effectivness of this important
activity.

\section{Implementation Roadmap}
The implementation of training should target multiple training formats and knowledge transfer, such as videos, wikis, lectures, jupyter notebooks and advanced visualizations, etc.
People who learn in non-conventional ways should not be excluded from the
opportunity to learn. Since there are different stages of knowledge transfer,
programs should be developed that encourage experts to share knowledge. Issues
considered in this section include global training initiatives, strategies for
leveraging existing forums, and training tool development.

>>>>

%____________________________________________________________________
%____________________________________________________________________
\section{Motivation}

@@

Within a single experiment, different skill sets are needed. In addition to a
skill set that contains basic programming language knowledge, testing and code
management tools, and experiment-specific framework knowledge, there are more
specialized skills that only a subset of the community needs to know, such as
software optimization, or low-level hardware interfaces.
While there already are experiment-specific training efforts in place, there are
many needs that are in common between experiments. Therefore, we should probably
strive to extract the common knowledge and build a common training program. This
would reduce duplication of efforts and enable growth of a shared training
culture by accumulating and sharing expertise across different experiments.
To realise this goal, a possibility could be the institution of a {\em
federation} of existing training initiatives, a very lightwheight umbrella just
aimed at improving the efficiency and cost-effectivness of this important
activity.

When trying to exchange training materials within a group the first problem is
to convince authors to contribute their work. This issue
can be alleviated with cautious intellectual property clauses. Another
problem is that trainers do not like to reuse given material as-is. They usually
want to refactor it, building their own training story.
This makes it difficult to have everyone agree on common material.
It is even challenging to agree to host material in the same
centralized place. A way to overcome this could be to settle for a centralized
catalog, with each author being free to host their material in their location
of choice.

Another challenge is the wide heterogeneity in
student competence. Special care must be given to setup
a training structure that can cope with both beginners and advanced students.
This may rest on a low granularity subdivision of independant topics.
The IN2P3 authors try to restrict their tutorials to 20 minutes
of material, as inspired by the Pomodoro technique, so that one can easily jump
and compose one's own ``menu''. However, it turns out to be tricky to keep such
small tutorials really independant and meaningful when they can be selected at
will.

All trainers have also faced the tremendous loss of time
in software installation for any practical exercises as many students have
not managed to prepare their machines in advance.
Here containers may bring real
progress, provided that everyone has at least Docker installed on their machine.
JupyterHub, also, is a technology which enable training session with
no need for installation (but with a need for network).

%____________________________________________________________________
%____________________________________________________________________
\section{Implementation Roadmap}
The implementation of training should target multiple training formats and knowledge transfer, such as videos, wikis, lectures, jupyter notebooks and advanced visualizations, etc.
People who learn in non-conventional ways should not be excluded from the
opportunity to learn. Since there are different stages of knowledge transfer,
programs should be developed that encourage experts to share knowledge. Issues
considered in this section include global training initiatives, strategies for
leveraging existing forums, and training tool development.
